### 2015-01-19 src/tables.Rnw
update

\begin{table*}[!ht]
<<tblsingles, child='tbl.singleop.Rnw'>>=
@
%\caption*{Single Operators}
\caption {The single operator selection strategy}
\label{tbl:singles}
\end{table*}

>>>>

\begin{table*}[!ht]
<<tblsingle,results='asis'>>=
norder <- c('nmc','rv','ic','dc','nc','rc','vmc','cc','emv','m','cb','i','ri','rs','es','in')
print(tbl.place(xtable(eff(s.singles.db[norder,]), caption='Single Operators', label='table:singles')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The single operator selection strategy}
\label{tbl:singles}
\end{table*}
